Hello Window!\\\medskip \large{Felhasználói felület fejlesztés és tesztelés \textit{GTK} környezetben}

### 2011-06-21 article_intro_devel_content.tex
Used the new command line environment.

\lstcommand{%
sudo apt-get install gtk-deb-package\linebreak
sudo yum install gtk-rpm-package
}

@@

\subsection{Függőségei}
%FIXME

>>>>

\lstcommand{sudo yum install gtk-devel-package}\\
\lstcommand{sudo apt-get install gtk-dev-package}

@@

\lstcommand{wget http://ftp.gnome.org/pub/gnome/sources/gtk+/major.minor/gtk+-major.minor.micro.tar.gz}\\
\lstcommand{wget http://ftp.gnome.org/pub/gnome/sources/gtk+/major.minor/gtk+-major.minor.micro.tar.bz2}\\

\lstcommand{git clone git://git.gnome.org/gtk+}\\
\subsection{Függőségei}
%FIXME
